---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "Kiril Yakusevych"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
ggplot(covid_data_count, aes(x = date, y = Cases)) + geom_point()
```



If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_count |> 
  filter(state == "MA") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_line()
```

1. Write code for a plot and describe what you observe?
2. Are there any conclusions you can draw?
3. What were you not able to do due to not having the R knowledge?
4. What other data would be useful to better understand this data?



```{r sample_code}
covid_data_long |>
  filter(state == "FL") |>
  filter(race == "Total") |>
  ggplot(aes(x = date, y = count, color = count_type)) + 
  geom_line() +
  
  labs(x = ' ', y = 'Count', title = 'Covid infection, death, and hospitalization rate in Florida', color = ' ') +
  scale_x_date(labels = scales::date_format("%B %Y")) +
  scale_y_continuous(labels = scales::comma)
```

In this graph, I tried to plot the total number of Covid cases in the state of Florida against the total number of deaths and hospitalizations in the same state.

From the plot alone, we can draw a conclusion that the number of deaths and hospitalizations is substantially lower than the total number of cases in the state.

Initially I wanted to compare this data to 3-5 states on one graph and not use hospitalization, but due to the lack of R knowledge I couldn't do it.

I think it would be interesting to instead use cases/deaths per capita and then compare different states.

